\documentclass[10pt]{article}
\usepackage[a4paper,left=2.54cm,top=2.54cm,right=2.54cm,bottom=2.54cm]{geometry}
\usepackage{fancyhdr}
\setlength{\headsep}{1.40cm} % Adjust the space after the header
\usepackage{afterpage}
\usepackage{setspace}
\usepackage{ICCFD/bibspacing}
\singlespacing

%%%% YOU CAN PUT YOUR OWN DEFINITIONS HERE
\newfont{\toto}{msbm10 at 12 pt}
\newfont{\ithd}{cmr9}
%%%% END OF YOUR DEFINITIONS 
 
\pagestyle{fancyplain}
\renewcommand{\headrulewidth}{0pt}

\usepackage{amsmath,amsthm,amsfonts,amssymb}
\usepackage[pdftex]{graphicx} 
\usepackage[T1]{fontenc}

%%%% additional packages
\usepackage{physics}
\usepackage{float}
\usepackage[hidelinks]{hyperref}
% \usepackage{hyperref} 
% \hypersetup{
%     colorlinks=true,
%     linkcolor=blue,
%     filecolor=magenta,       
%     urlcolor=cyan, 
%     } 
\usepackage{subcaption}

%%%% CONFERENCE HEADER. REPLACE xxxx WITH 4-DIGIT PAPER NUMBER ASSIGNED BY CONFERENCE COMMITTEE.

\rhead{\ithd{\bf ICCFD12-2024-xxxx\\  \   \\}}
\lhead{\ithd{\bf Twelfth International Conference on \\      
Computational Fluid Dynamics (ICCFD12), \\
Kobe, Japan, July 14-19, 2024
}}
% Define the left and center headers to be empty or contain fixed content
\rhead{} 
\chead{}

\usepackage{titling}
\setlength{\droptitle}{0em}  
\pretitle{\vspace{-4em}\begin{center}\LARGE}
\posttitle{\end{center}\vspace{-1em}}
\preauthor{\begin{center}\large}
\postauthor{\end{center}\vspace{-3em}}


\title{
    \bf 
    High-order Accurate Implicit Scheme Based on 
    Temporal Reconstruction for Solving Compressible 
    Navier-Stokes Equations 
}
\author{
Hanyu Zhou$^{*}$, Yu-Xin Ren$^{*,**}$ \\
$^{*}$ Department of Engineering Mechanics, Tsinghua University, Beijing, 100084,    China.
$^{**}$Corresponding author: ryx@tsinghua.edu.cn
}
\date{}

\begin{document}

%%%% TITLE
\maketitle
\afterpage{\fancyhead{}}

%%%% ABSTRACT AND KEYWORDS
%\vskip0.5cm
\centerline{
    \begin{minipage}[t]{150mm}
        {\bf Abstract:}
        A family of new implicit time marching schemes based on 
        Direct Integration and Temporal 
        Reconstruction (DITR) is developed and tested in this paper.
        These schemes can be used to solve ordinary differential equations (ODEs)
        directly or solve ODEs arising from semi-discrete schemes
        solving partial differential equations (PDEs),
        including the compressible Navier-Stokes equations.
        The most significant advantages of these methods are that temporally third- and fourth-order
        schemes can be constructed straightforwardly, 
        and require fewer stages than some popular implicit Runge-Kutta schemes. 
        As an ODE solver, the DITR method are found to be 
        $A$-stable, with two variants of them being $L$-stable. 
        A matrix-free iteration method for solving the DITR equations
        is described for practical implementation of DITR. 
        Numerical results show that 
        DITR methods achieve high order of accuracy 
        with comparatively 
        lower computational cost.
        When reaching the same error, 
        some DITR methods are able to 
        save significant amount of time
        compared with the implicit ESDIRK4 method. 
        \vskip0.2cm 
        {\it Keywords:} High-order Methods, Time Marching, Temporal Reconstruction, Unsteady Flows. \\
    \end{minipage}
}



\vskip0.5cm

%%%% MAIN PART


\input{HM3Draft_Defs.tex}
\input{HM3Draft_ICCFD_Content.tex}

%%%% BIBLIOGRAPHY
\bibspacing=\dimen 100
\bibliographystyle{unsrt}
\bibliography{HM3DraftRefs}

\end{document}
